Type-theoretical Semantics of \Pio\ via the Delay Monad \thanks{Supported by organization x.}

### 2019-04-24 mpc19/paper.tex
Added some TODOs!

@@

@@

\section{Introduction}\label{sec:intro}

>>>>

\usepackage{soul}

@@

\newcommand{\todo}[1]{\hl{TODO: #1}}
\newcommand{\todocite}[1]{\hl{[TODO: #1]}}

@@

\section{TODO} % (fold)
\label{sec:todo}
Robin:
\begin{itemize}
  \item Abstract.
  \item Introduction.
  \item Check and correct 4.1, 4.2, add citations, etc.
  \item Make pictures! 
  \begin{itemize}
    \item Graphical language of monoidal categories, and for \Pio.
    \item Trace.
    \item Iterator, iterator unfolding axiom.
    \item Trace from iterator.
  \end{itemize}
  \item Conclusion
  \begin{itemize}
    \item Related work: Kleisli category of the Delay monad is a join
    restriction category, inverse category of a join restriction category is a
    join inverse category; already known to be dagger-traced under certain
    conditions.
    \item Future work: Semantics of time invertible programming. Extension of
    the work on the Kleisli category of the Delay monad beyond $\Set$ to other
    (more general) categories, e.g. topoi.
  \end{itemize}
\end{itemize}
Niccolò: 
\begin{itemize}
  \item Fix the syntax to be closer to ordinary presentations (but do describe 
  how it is realized in Agda).
  \item Finish the section about trace and iteration.
  \item Remind the reader about double lines of coinductive definitions. 
\end{itemize}
Both:
\begin{itemize}
  \item \textbf{Important:} Come up with a punnier title! (Something about 
  delays and daggers).
\end{itemize}
% section todo (end)

\section{Introduction}\label{sec:intro}
\todo{RC Motivation.}

\todo{Formalization motivation? Maybe?}

\todo{Explain Carette et al. Say that we are extending it to be actually useful (but don't say it like that).}

\todo{Delay vs. Maybe monad.}
